---
title: "Double Reactivity"
author: "Andreas Tonio Liebrand"
date: "26. August 2016"
output: html_document
runtime: shiny
---

## Case 1: The sales team

You are the leader of a sales team with three employees, who sell four products. 
To monitor the success of your team important key figures are the overall earnings as well as the earnings per product. 

The following Rshiny+d3.js plot can answer four questions: 

* Question 1: What are the overall earnings per person? (bar chart)

* Question 2: How high (absolute/relative) are the overall earnings aggregated per category? (circle and table)

* Question 3: How high (absolute/relative) are the overall earnings per category for each person? (Mouseover on the bars)

* Question 4: How high are the absolute earnings  per person related to each other given a category? (Mouseover on the circle)

```{r, echo=FALSE}
shinyAppDir(
  "./DoubleReactivity_Simple"
 , options=list(
   width="1400px", height="800px"
 )
)
```

## Case 2: Using R Charts

R-User might be interested to customize the chart by using R plots. An example can be seen next, where data is split in groups which aggregated amount can be seen in the pie chart, while a mouseover on the pie chart shows the data distribution within each group.
```{r, echo=FALSE}
shinyAppDir(
  "./d3_BarChart_Circles_RPlot"
 , options=list(
   width="1400px", height="800px"
 )
)
```



## Remarks
The java script code is developed by [NPashaP](http://bl.ocks.org/NPashaP) and can be found [here](http://bl.ocks.org/NPashaP/96447623ef4d342ee09b).